Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-20 manuscript.Rmd
peer review comments

```{r, include = FALSE}
# import functions
source("functions.R")

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```

@@

sjPlot::tab_model(null1)
```

@@

>>>>

```{r, include = FALSE}
# import functions
source("functions.R") #this is a cool way to use another script, thanks!

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)

#this table can have the same formatting as others.
```

@@

sjPlot::tab_model(null1) #nice package fot tables
```

@@

<!-- Peer review -->

<!-- I really liked the look and feel of your manuscript! `.tabset-fade` had a nice look. Also thanks for introducing the `source()` function and `the sjPlot::tab_model()` - I can see myself using these. Sometimes when reporting statistic and equaltions in the markdown, I prefer using the latex format. Basically by enclosing in single dollar sign or double dollar sign (puts it in a new line) So, $M_{age}$, or $$M_{age}$$. Good luck with the manuscript.  -->
